---
title: "Multihop Rendezvous"
author: "John Pavlik"
date: "Monday, August 31, 2015"
output: beamer_presentation
---
```{r, echo=FALSE}
library(ggplot2)
library(xlsx)
drseq = read.xlsx("C:/Users/John/git/CR-Simulator/Simple CR Simulator/Aggregated.xlsx", sheetName="DRSEQ")
ejs = read.xlsx("C:/Users/John/git/CR-Simulator/Simple CR Simulator/Aggregated.xlsx", sheetName="EJS")
data = data.frame(drseq, ejs)
```
## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3


## Slide with Plot

```{r, echo=FALSE}

longdrseq = reshape(drseq, 
        varying=c("X10","X20","X30","X40","X50","X60","X70","X80","X90","X100","X250","X500","X750","X1000"),
        v.names="Time",
        timevar="Channels",
        times=c("X10","X20","X30","X40","X50","X60","X70","X80","X90","X100","X250","X500","X750","X1000"),
        direction="long")
longdrseq1.100=subset(longdrseq, longdrseq$Channels!="X100" & longdrseq$Channels!="X250" & longdrseq$Channels !="X500" & longdrseq$Channels != "X750" & longdrseq$Channels != "X1000")
qplot(data=longdrseq1.100, x=Channels,y=Time, geom="line") 
help(reshape)
```

